---
title: "000_Install_packages"
output: html_document
---

```{bash}
sudo apt-get update -y 
sudo apt-get install -y libbz2-dev
sudo apt-get install -y liblzma-dev
```

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install(version = '3.11')
BiocManager::install("dada2", version = "3.11")

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("dada2", version = "3.11")

BiocManager::install("phangorn")
BiocManager::install("DECIPHER")

install.packages("gridExtra")

ps_connect <-url("https://raw.githubusercontent.com/spholmes/F1000_workflow/master/data/ps.rds")
ps = readRDS(ps_connect)
ps

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("Bioconductor")

.cran_packages <- c( "shiny","miniUI", "caret", "pls", "e1071", "ggplot2", "randomForest", "dplyr", "ggrepel", "nlme", "devtools",
                  "reshape2", "PMA", "structSSI", "ade4",
                  "ggnetwork", "intergraph", "scales")
.github_packages <- c("jfukuyama/phyloseqGraphTest")
.bioc_packages <- c("genefilter", "impute")

install.packages(.cran_packages)
devtools::install_github(.github_packages)
BiocManager::install(.bioc_packages)
```

```{r}
BiocManager::install("DESeq2")
```


install.packages("structSSI")
library("structSSI")

library(devtools)
install_local("./structSSI_1.1.1.tar.gz")

wget https://cran.r-project.org/src/contrib/Archive/structSSI/structSSI_1.1.1.tar.gz
```

```{bash}
if (! requireNamespace ("BiocManager", tranquillement = TRUE))
    install.packages ("BiocManager")

BiocManager :: install ("phyloseq")
```

```{r}
if (! requireNamespace ("BiocManager", tranquillement = TRUE))
    install.packages ("BiocManager")

BiocManager :: install ()
```
```{r}
source('http://bioconductor.org/biocLite.R')
biocLite('phyloseq')
```
```{bash}
source("https://raw.githubusercontent.com/joey711/phyloseq/master/inst/scripts/installer.R",
       local = TRUE)
```

